Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-06-23 lqg-strings.tex
made some changes in your section, your appendices and in the introduction

In \autoref{sec:inverse-metric-Polyakov} we explore the Polyakov version of the modified string action derived from the bimetric analysis and point out its consequences for the equations of motion. We also take a glance at the explicit expression for the $\Delta _{a b}$ field by considering the (area-corrected) string coupled to the Kalb-Ramond field. Furthermore, we solve the string equations of motion for a particular case of constant-coefficient to find the fundamental modes and derive the Poisson bracket algebra for the modes and constraints. In \autoref{sec:quantum-kg-string} we follow the route of canonical covariant quantization for the solution previously found and discuss the consequences of our area-corrected model regarding the dimensionality of the background spacetime and the presence of negative-norm states (ghosts) in the physical excitations.

@@

The Nambu-Goto area-corrected action before approximations \eqref{eqn:NG-area-corrected} has a structure strikingly similar to the Born-Infeld model \cite{Bergshoeff1987BornInfeld,Leigh1989Dirac-Born-Infeld,Metsaev1987Borninfeld,Tseytlin1996Self-Duality}, which arises in the string theory description of gauge fields living on D-branes:
\begin{equation} \label{eqn:BI-action}
	S_{B I} = - T \int \diff ^p x \sqrt{- \det (\gamma _{a b} + 2 \pi \alpha ' F_{a b})} ,
\end{equation}
with $T$ being the tension of the $p$-brane, $\gamma _{a b}$ is the pullback metric of said brane, $F_{a b}$ is the pullback of the field strength of the gauge field and $2 \pi \alpha '$ the inverse tension of the string. Remarkably, if one considers a $(1 + 1)$-dimensional Born-Infeld action with $2 \pi \alpha ' F_{a b} = \sqrt{k} \Delta _{a b}$, it can be shown that
\begin{equation} \label{eqn:area-corrected-NG-BI-equivalence}
	\det (h_{a b} + \sqrt{k} \Delta _{a b}) \equiv h + k \Delta ,
\end{equation}
thus the action \eqref{eqn:NG-area-corrected} can be recast as a Born-Infeld model for the string with $k$ playing the role of inverse tension squared and $\Delta _{a b}$ the role of the pullback of a field strength. Since we explored the relation between $\Delta _{a b}$ and the Kalb-Ramond field $B_{\mu \nu}$ in \autoref{sec:WS-Kalb-Ramond-QoA}, this could mean that the Kalb-Ramond 2-form is exact, $B = \diff A$, and thus its exterior derivative, which gives the torsion of the background spacetime \cite{Tong2009Lectures}, vanishes $\diff B = \diff (\diff A) = 0$. Also, we have a direct relation between string tension and scale
\begin{equation} \label{eqn:k-T}
	\frac{l_p}{l_s} = k \sim (2 \pi \alpha ')^2 = \frac{1}{T^2} .
\end{equation}

@@

Afshordi's work notes that the action \eqref{eqn:emergent-dimensions-action} only has background Poincaré invariance and WS Weyl symmetry as approximate symmetries for the fields with $m_{\mu} \gg T$, thus the \textquotedblleft emergent spacetime and evolving dimensions" by interpreting the fields with effective mass as being inaccessible due to not obeying Poincaré symmetry. We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0} , m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, in agreement with \cite{t-Hooft1993Dimensional}. $(2 + 1)$-dimensional gravity has already been successfully quantized before (\cite{Bergshoeff2013ZweiDreibein},\cite{Blais2013A-new-quantization},\cite{Witten1998Anti},\cite{Carlip2003Quantum}). We thus postulate that $m_{3} \sim T_{pl}$, which together with the constraints \eqref{eqn:X-masses-constraint} should give us a way to calculate the other mass parameters given the WS energy and momentum of the fields, making it possible to predict in which scales the other dimensions should start to open up.

@@

Uptil now we have studied a phenomenological modification of the string action. However, ultimately all phenomenological ideas must have a grounding in some exact, microscopic description of the system. Further, we have neglected one very important aspect of this whole endeavor, which is the description of the background geometry in the connection formalism and how to couple that geometry to the geometry of the string worldsheet. In this section we present a possible action for the bosonic string in which the effect of the bulk geometry on the worldsheet is encoded in the string action in terms of a connection which lives on the worldsheet, but takes values in the Lie algebra of the gauge group which is being used to describe the bulk geometry.  We will explore the natural consequences which follow from considering the symmetries of such an action.

First let us recall the form of the Polyakov action for the bosonic string \eqref{eqn:polyakov-action}:
\begin{equation*}
	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
\end{equation*}
If one was to ask a beginning graduate student as to how one can incorporate a gauge field in the above expression, the natural answer would be that we can promote the $X^\mu$ to vectors which live in the representation of some gauge group $\mc G$ and promote the ordinary derivative to a gauge covariant derivative \wrt a connection valued in $\mc G$. The resulting action would now have the form:
\begin{equation}\label{eqn:polyakov-gauged}
	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \mc{D}_a X^\mu \mc{D}_b X^\nu \eta_{\mu\nu},
\end{equation}
where the covariant derivative $\mc{D}_a$ is of the form:
\begin{equation}\label{eqn:covariant-deriv-v1}
	\mc{D}_a X^\mu(\tau , \sigma) = \partial_a X^\mu + g \mc{A}_{a}^\mu{}_\nu X^\nu,
\end{equation}
where $\mc{A}_{a}^\mu{}_\nu$ is the gauge field and $g$ is the gauge coupling. A more experienced researcher would object saying that we know that the $X^\mu$ are spacetime co-ordinates and not vectors transforming under the gauge group $\mc G$. But we will see that this is not a problem. In fact, in order to be able to couple the string to an \emph{arbitrarily} curved geometry we will find that we \emph{require} the $X^\mu$ to transform as vectors under the action of some \emph{local} gauge field.

Our goal is to write down the action of a string propagating in a background geometry. One might argue that the expression \eqref{eqn:polyakov-gravity}, where we replace the bulk Minkowski tensor $\eta_{\mu\nu}$ with an arbitrary tensor $G_{\mu\nu}$ which tells us what the components of the bulk metric are at that point on the worldsheet. However, we view this approach as unsatisfactory, not the least because it does not allow us to make contact of the string action with a background geometry specified in terms of connection variables instead of metric ones. An astute reader might correctly object saying that we can simply replace $G_{\mu\nu}$ in \eqref{eqn:polyakov-gravity} with $\tilde E_\mu^I \tilde E_\nu^J \eta_{IJ}$ (here $\eta_{IJ}$ is now the Minkowski metric in locally flat co-ordinates). This, however, leaves open the question of what role the bulk connection should play in this picture.

@@

Therefore, now we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\mc{A}_{a}^{ij}$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$. $X^\mu(\tau , \sigma)$ are the space-time coordinates of a point $(\tau , \sigma)$ on the worldsheet. Now if one adopts the ``sigma model'' point of view then the $X$'s can be viewed as $d+1$ scalar fields living on a $1+1$ worldsheet. But we know that these fields are not a collection of $d+1$ independent scalars. They are components of a $d+1$ dim vector since they transform with the fundamental representation of $\mathrm{SO}(d,1)$ under global Lorentz transformations acting on the ambient space-time. However, the symmetries of a flat background include not only Lorentz transformations bulk also translations. The string action is required to be invariant under both of these:
\begin{subequations}\label{eqn:poincare-symmetries}
	\begin{align}
		X^\mu & \rarrow X^\mu + \delta X^\mu; \quad \delta X^\mu \in \mbb{R}^{3,1}            \\
		X^\mu & \rarrow \Lambda^\mu{}_\nu X^\mu; \quad \Lambda^\mu{}_\nu \in \mathrm{SO}(3,1)
	\end{align}
\end{subequations}
where $\delta X^\mu$ is some arbitrary vector in Minkowski space. The semidirect product of $\mbb{R}^{3,1}$ with $\mathrm{SO}(3,1)$ is $ISO^{3,1}$, the Poincaré group in $3+1$ dimensions. Of course, these are good symmetries only if our background is flat. An arbitrarily curved background can have one or more Killing vectors depending on how much symmetry the geometry has, but \emph{in general} even that need not be the case. The best one can hope for is some notion of local flatness is some finite subregion of the background manifold. Moreoever the entire purpose of this work to try and understand how to write down a string action in an \emph{arbitrarily curved} background, assuming that such a thing is even possible.

@@

However, diffeomorphisms and gauge transformations are not independent of each other. A diffeomorphism is a differentiable map from one manifold to another (in the case of general relativity both manifolds are generally taken to be the same), which has a differentiable (and invertible) map. In more pedestrian language, a diffeomorphism is an (invertible) change of co-ordinates on a manifold. A gauge transformation is a redefinition of the local fields which live on the underlying manifold. In fact, at least for certain geometries, these two can be seen to be equivalent to each other, with diffeomorphisms representing ``passive'' co-ordinate transformations and gauge representing ``active'' co-ordinate transformations.

@@

Instead of viewing the $X$'s as elements of a Minkowski space, we think of them as elements of the tangent space $T_p (M)$ at a given point $p$ of the background manifold $M$.

@@

This viewpoint on the embedding fields, as elements of the tangent space $T_p(M)$, might appear to be at odds with their prescribed usage as co-ordinate functions on $M$. However, some reflection shows that this is not the case. For instance, one can take the embedding manifold to be a two-dimensional sphere $S^2$. Then the co-ordinates of a point on the string worldsheet $\Sigma$ can be expressed in terms of the polar and azimuthal angles $\theta$ and $\phi$. The action for this system would be:
\begin{equation}\label{eqn:s2-string}
	S_{S^2} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \partial_a \theta^\mu \partial_b \theta^\nu G_{\mu\nu},
\end{equation}
where $\theta^\mu(\sigma,\tau) \in \{\theta, \phi\}$ are the embedding fields, and $G_{\mu\nu}$ is \emph{a} metric living on $S^2$.

@@

This is where we run into a problem. There is no way to express infinitesimal translations in $d+1$ dimensions as the action of a $d+1$ dimensional matrix valued group on a point living in $\mbb{R}^{d+1}$. In order to incorporate translations we have to resort to a trick and introduce an extra ``dummy'' dimension for the background manifold. Now we have $d+2$ embedding fields which we can write as:
\begin{equation}
	X^A := \{X^0, \vec X, X^r\} = \{X^\mu, X^r\},
\end{equation}
where $X^\mu = \{X^0, \vec X\}$ are the fields we had originally and $X^r$ is our new ``dummy'' co-ordinate. As we will see this dimension will turn out to have a very important physical interpretation in the context of Einstein-Cartan geometry.

@@

Now, one proceeds in the usual way by determining the symmetries of the action \eqref{eqn:polyakov-flat}, varying the action to find the equations of motion, fixing the gauge using the Weyl freedom of the worldsheet and then solving the classical equations of motion. Imposition of (bosonic) commutation relations on the operator versions of the embedding fields $\hat X^\mu$ then leads us to description of the quantum state of the bosonic string in terms of an infinite ladder of harmonic oscillators which obey the Virasoro algebra.

The obvious drawback of this approach is that the background metric is non-dynamical and is fixed to be the flat Minkowski metric $\eta_{\mu\nu}$. Clearly, one would like to be able to understand the physics of a string propagating on an arbitrary curved background. It wouldn't make much sense to refer to string theory as a theory of ``quantum gravity'' if strings can only be described on flat backgrounds. The way this is accomplished is by treating the metric of the worldvolume as a ``background field'' $G_{\mu\nu}$, in terms of which the Polyakov action becomes:
\begin{equation}\label{eqn:polyakov-gravity}
	S'_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu}(X),
\end{equation}
where the bulk metric is now a function of the bulk co-ordinates $G_{\mu\nu}(X)$. Now this metric is still non-dynamical because the action \eqref{eqn:polyakov-gravity} does not contain any terms with time derivatives of $G_{\mu\nu}$. However, if we view the action purely as a two-dimensional theory of $D$ scalar fields, then the bulk metric can be viewed as a collection of \emph{coupling constants}, rather than a dynamical entity which exists independent of the string. One can now proceed in the usual manner for any field theory and calculate the beta function of the coupling constants of the theory as a function of the energy scale.

Then, as shown long ago by Friedan \cite{Friedan1985Nonlinear} (see also \cite{Callan1989Sigma}, \cite{Callan1985Strings} or \cite[Sec 3.7]{Polchinski1998aString}, \cite[Sec 7.2]{Tong2010Lectures} for a more pedagogical explanation), that the garviton beta function is proportional to $R_{\mu\nu}$, the Ricci curvature of the bulk geometry. The requirement of Weyl invariance of the string worldsheet implies that this beta function should vanish:
\begin{equation}\label{eqn:ricci-flat}
	\beta(G_{\mu\nu}) \propto R_{\mu\nu} = 0.
\end{equation}
Therefore we find that conformal invariance of the string worldsheet \emph{implies} that the background geometry in which the string propagates satisfies the \emph{vacuum} Einstein equations. It is this result which is often cited as evidence for the claim that string theory is a \emph{background independent} theory of quantum gravity.

@@

There is another explanation for why it makes sense to promote the $X$'s to local fields. This can be found in terms of the expression for the area of a 2-surface. We have a manifold $\mc M$, within which is embedded a two dimensional submanifold $\mc N$. Let $(\tau,\sigma)$ be the location of a point on the worldsheet and $X^\mu(\tau, \sigma)$ be the location of that same point in terms of co-ordinates on $\mc M$. Then we can define the induced metric on $\mc N$, $h_{ab}$ in terms of the embedding fields and their derivatives:

\begin{equation}\label{eqn:ws-metric}
	h_{ab} = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} g_{\mu\nu},
\end{equation}
where $g_{\mu\nu}$ is the metric in the ambient space $\mc M$. Now, we can calculate the area of a small patch of $\mc P \in \mc N$ by taking the square root of the determinant of the induced metric $\sqrt{\det(h)}$ and integrating over that patch:
\begin{equation}\label{eqn:patch-area-v1}
	A^{(1)}_{\mc P} = \int_{\mc P} d^2 x \, \sqrt{\det(h)}.
\end{equation}
This is, of course, the expression for the Nambu-Goto action - modulo some constants - which we all know and love. In LQG we don't have a notion of embedding fields. Since we are dealing with gauge invariant observables constructed from holonomies of a connection along a 1d-curve and the flux of a tetrad across a 2-surface, the embedding co-ordinates of the curves and surface turn to not be needed. When promoting classical observables into quantum operators acting on lines and surfaces the embedding co-ordinates of the lines and surfaces are not relevant as long as we work with gauge invariant quantities.

How then does one define the area of a surface in LQG? It is defined as the magnitude of the area two form. Recall that given a tetradic basis $e_\mu^I$ for a local Lorentz frame whose metric is given by $g_{\mu\nu}$, we can write the metric in terms of the tetrad in the usual manner:
\begin{equation}\label{eqn:metric-from-tetrad}
	g_{\mu\nu} = e_\mu^I e_\nu^J \eta_{IJ},
\end{equation}
where $\eta_{IJ}$ is the flat Minkowski metric on the ``internal'' flat space. If we consider any two dimensional surface in the local Lorentz frame, then its area can be written in terms of the vielbein as:
\begin{equation}
	A^{(2)}_{\mc P} = \int_{\mc P} \Tr (e_\mu \wedge e_\nu) dx^\mu \wedge dx^\nu,
\end{equation}
the trace is taken over the ``internal'' Lorentz indices.

Now, if we compare the two expressions \eqref{eqn:ws-metric} and \eqref{eqn:metric-from-tetrad} we notice an obvious parallel between the derivatives $\partial X^\mu/\partial x_a$ of the embedding co-ordinates and the vielbein $e_\mu^I$. This similarity becomes more apparent once we write down the expression for the area of a 2-surface by taking the determinant in \eqref{eqn:patch-area-v1} and comparing that to the expression obtained using frame fields.

>>>>

In \autoref{sec:inverse-metric-Polyakov} we explore the Polyakov version of the modified string action derived from the bimetric analysis and point out its consequences for the equations of motion. We also take a glance at the explicit expression for the $\Delta _{a b}$ field by considering the (area-corrected) string coupled to the Kalb-Ramond field. Furthermore, we explore an equivalence between our proposed model and the Born-Infeld model in $1 + 1$ dimensions. We conclude this section by solving the string equations of motion for a particular case of constant-coefficient to find the fundamental modes and derive the Poisson bracket algebra for the modes and constraints. In \autoref{sec:quantum-kg-string} we follow the route of covariant quantization for the solution previously found and discuss the consequences of our area-corrected model regarding the dimensionality of the background spacetime and the presence of negative-norm states (ghosts) in the physical excitations.

@@

The Nambu-Goto area-corrected action before approximations \eqref{eqn:NG-area-corrected} has a structure strikingly similar to the Born-Infeld model \cite{Bergshoeff1987BornInfeld,Leigh1989Dirac-Born-Infeld,Metsaev1987Borninfeld,Tseytlin1996Self-Duality}, which arises in the string theory description of gauge fields living on D-branes:
\begin{equation} \label{eqn:BI-action}
	S_{B I} = - T \int \diff ^p x \sqrt{- \det (\gamma _{a b} + 2 \pi \alpha ' F_{a b})} ,
\end{equation}
with $T$ being the tension of the $p$-brane, $\gamma _{a b}$ is the pullback metric of said brane, $F_{a b}$ is the pullback of the field strength of the gauge field and $2 \pi \alpha '$ the inverse tension of the string. Remarkably, if one considers a $(1 + 1)$-dimensional Born-Infeld action with $2 \pi \alpha ' F_{a b} = \sqrt{k} \Delta _{a b}$, it can be shown that
\begin{equation} \label{eqn:area-corrected-NG-BI-equivalence}
	\det (h_{a b} + \sqrt{k} \Delta _{a b}) \equiv h + k \Delta ,
\end{equation}
thus the action \eqref{eqn:NG-area-corrected} can be recast as a Born-Infeld model for the string with $k$ playing the role of inverse tension squared and $\Delta _{a b}$ the role of the pullback of a field strength. Since we explored the relation between $\Delta _{a b}$ and the Kalb-Ramond field $B_{\mu \nu}$ in \autoref{sec:WS-Kalb-Ramond-QoA}, this could mean that the Kalb-Ramond 2-form is exact, $B = \diff A$, and thus its exterior derivative, which gives the torsion of the background spacetime \cite{Tong2009Lectures}, vanishes $\diff B = \diff (\diff A) = 0$. Also, we have a direct relation between string tension and scale
\begin{equation} \label{eqn:k-T}
	\frac{l_{pl}}{l_s} = k \sim (2 \pi \alpha ')^2 = \frac{1}{T^2} .
\end{equation}

@@

Afshordi's work notes that the action \eqref{eqn:emergent-dimensions-action} only has background Poincaré invariance and WS Weyl symmetry as approximate symmetries for the fields with $m_{\mu} \gg T$, thus the \textquotedblleft emergent spacetime and evolving dimensions" by interpreting the fields with effective mass as being inaccessible due to not obeying Poincaré symmetry. We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0} , m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, in agreement with \cite{t-Hooft1993Dimensional}. $(2 + 1)$-dimensional gravity has already been successfully quantized before (\cite{Bergshoeff2013ZweiDreibein},\cite{Blais2013A-new-quantization},\cite{Carlip2003Quantum}). We thus postulate that $m_{3} \sim T_{pl}$, which together with the constraints \eqref{eqn:X-masses-constraint} should give us a way to calculate the other mass parameters given the WS energy and momentum of the fields, making it possible to predict in which scales the other dimensions should start to open up.

@@

Until now we have studied a phenomenological modification of the string action. However, ultimately all phenomenological ideas must have a grounding in some exact, microscopic description of the system. Further, we have neglected one very important aspect of this whole endeavor, which is the description of the background geometry in the connection formalism and how to couple that geometry to the geometry of the string worldsheet. In this section, we present a possible action for the bosonic string in which the effect of the bulk geometry on the worldsheet is encoded in the string action in terms of a connection which lives on the worldsheet but takes values in the Lie algebra of the gauge group which is being used to describe the bulk geometry.  We will explore the natural consequences which follow from considering the symmetries of such an action.

First let us recall the form of the Polyakov action for the bosonic string \eqref{eqn:polyakov-action}:
\begin{equation*}
	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
\end{equation*}
If one was to ask a beginning graduate student as to how one can incorporate a gauge field in the above expression, the natural answer would be that we can promote the $X^\mu$ to vectors which live in the representation of some gauge group $\mc G$ and promote the ordinary derivative to a gauge covariant derivative \wrt a connection valued in $\mc G$. The resulting action would now have the form:
\begin{equation}\label{eqn:polyakov-gauged}
	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \mc{D}_a X^\mu \mc{D}_b X^\nu \eta_{\mu\nu},
\end{equation}
where the covariant derivative $\mc{D}_a$ is of the form:
\begin{equation}\label{eqn:covariant-deriv-v1}
	\mc{D}_a X^\mu(\tau , \sigma) = \partial_a X^\mu + k \mc{A}_{a}^\mu{}_\nu X^\nu,
\end{equation}
where $\mc{A}_{a}^\mu{}_\nu$ is the gauge field and $k$ is the gauge coupling. A more experienced researcher would object saying that we know that the $X^\mu$ are spacetime co-ordinates and not vectors transforming under the gauge group $\mc G$. But we will see that this is not a problem. In fact, in order to be able to couple the string to an \emph{arbitrarily} curved geometry we will find that we \emph{require} the $X^\mu$ to transform as vectors under the action of some \emph{local} gauge field.

Our goal is to write down the action of a string propagating in a background geometry. One might argue that the expression \eqref{eqn:polyakov-gravity}, where we replace the bulk Minkowski tensor $\eta_{\mu\nu}$ with an arbitrary tensor $G_{\mu\nu}$ which tells us what the components of the bulk metric are at that point on the worldsheet already describes the string in an arbitrary background geometry. However, we view this approach as unsatisfactory, not the least because it does not allow us to make contact of the string action with a background geometry specified in terms of connection variables instead of metric ones. An astute reader might correctly object saying that we can simply replace $G_{\mu\nu}$ in \eqref{eqn:polyakov-gravity} with $E_\mu^I E_\nu^J \eta_{IJ}$ (here $\eta_{IJ}$ is now the Minkowski metric in locally flat coordinates). This, however, leaves open the question of what role the bulk connection should play in this picture.

@@

Therefore, now we will require that the bulk connection $\mc{A}_{\mu} ^{I J}$ and the bulk vielbein $E^{\mu} _{I}$ can be pulled back onto a connection $\mc{A}_{a}^{I J}$ and a dyad $e^a_I$, respectively, living on the string worldsheet $\Sigma$. $X^\mu(\tau , \sigma)$ are the space-time coordinates of a point $(\tau , \sigma)$ on the worldsheet. Now if one adopts the ``sigma model'' point of view then the $X$'s can be viewed as $d+1$ scalar fields living on a $1+1$ worldsheet. But we know that these fields are not a collection of $d+1$ independent scalars. They are components of a $d+1$ dim vector since they transform with the fundamental representation of $\mathrm{SO}(d,1)$ under global Lorentz transformations acting on the ambient space-time. However, the symmetries of a flat background include not only Lorentz transformations bulk also translations. The string action is required to be invariant under both of these:
\begin{subequations}\label{eqn:poincare-symmetries}
	\begin{align}
		X^\mu & \rarrow X^\mu + \delta X^\mu; \quad \delta X^\mu \in \mbb{R}^{3,1}            \\
		X^\mu & \rarrow \Lambda^\mu{}_\nu X^\mu; \quad \Lambda^\mu{}_\nu \in \mathrm{SO}(3,1)
	\end{align}
\end{subequations}
where $\delta X^\mu$ is some arbitrary vector in Minkowski space. The semidirect product of $\mbb{R}^{3,1}$ with $\mathrm{SO}(3,1)$ is $ISO^{3,1}$, the Poincaré group in $3+1$ dimensions. Of course, these are good symmetries only if our background is flat. An arbitrarily curved background can have one or more Killing vectors depending on how much symmetry the geometry has, but \emph{in general} even that need not be the case. The best one can hope for is some notion of local flatness is some finite subregion of the background manifold. Moreoever the entire purpose of this work to try and understand how to write down a string action in an \emph{arbitrarily curved} background, assuming that such a thing is even possible.

@@

However, diffeomorphisms and gauge transformations are not distinct concepts. A diffeomorphism is a differentiable map from one manifold to another (in the case of general relativity both manifolds are generally taken to be the same), which is a differentiable (and invertible, with inverse also differentiable) map. In more pedestrian language, a diffeomorphism from $\mc{M}$ to itself is an (invertible) change of coordinates on a manifold $\mc{M}$. A gauge transformation is a redefinition of the local fields which live on the underlying manifold. In fact, at least for certain geometries, these two can be seen to be equivalent to each other, with diffeomorphisms representing ``passive'' coordinate transformations and gauge representing ``active'' coordinate transformations. From the viewpoint of the formalism of Principal Fiber Bundles, where the gauge symmetry arises from a structure that locally looks like a Cartesian product of the base manifold $\mc{M}$ and the gauge group $G$, $\mc{M} \times G$, gauge transformation arise from local reparameterizations of the group component at each point of the base manifold, so it is a diffeomorphism in the \textquotedblleft enlarged" space $\mc{M} \times G$.

@@

Instead of viewing the fields $X^{\mu}$ as elements of a Minkowski space, we think of them as elements of the tangent space $T_p (M)$ at a given point $p$ of the background manifold $M$.

@@

This viewpoint on the embedding fields, as elements of the tangent space $T_p(M)$, might appear to be at odds with their prescribed usage as co-ordinate functions on $M$. However, some reflection shows that this is not the case. For instance, one can take the embedding manifold to be a two-dimensional sphere $S^2$. Then the coordinates of a point on the string worldsheet $\Sigma$ can be expressed in terms of the polar and azimuthal angles $\theta$ and $\phi$. The action for this system would be:
\begin{equation}\label{eqn:s2-string}
	S_{S^2} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \partial_a \theta^\mu \partial_b \theta^\nu G_{\mu\nu},
\end{equation}
where $\theta^\mu(\sigma,\tau) \in \{\theta, \phi\}$ are the embedding fields, and $G_{\mu\nu}$ is \emph{a} metric living on $S^2$.

@@

This is where we run into a problem. There is no way to express infinitesimal translations in $d+1$ dimensions as the action of a $d+1$ dimensional matrix-valued group on a point living in $\mbb{R}^{d+1}$. In order to incorporate translations we have to resort to a trick and introduce an extra ``dummy'' dimension for the background manifold. Now we have $d+2$ embedding fields which we can write as:
\begin{equation}
	X^A := \{X^0, \vec X, X^r\} = \{X^\mu, X^r\},
\end{equation}
where $X^\mu = \{X^0, \vec X\}$ are the fields we had originally and $X^r$ is our new ``dummy'' co-ordinate. As we will see this dimension will turn out to have a very important physical interpretation in the context of Einstein-Cartan geometry.

@@

Now, one proceeds in the usual way by determining the symmetries of the action \eqref{eqn:polyakov-flat}, varying the action to find the equations of motion, fixing the gauge using the Weyl freedom of the worldsheet and then solving the classical equations of motion. Imposition of (bosonic) commutation relations on the operator versions of the embedding fields $\hat X^\mu$ then leads us to the description of the quantum state of the bosonic string in terms of an infinite ladder of harmonic oscillators which obey the Virasoro algebra.

The obvious drawback of this approach is that the background metric is non-dynamical and is fixed to be the flat Minkowski metric $\eta_{\mu\nu}$. Clearly, one would like to be able to understand the physics of a string propagating on an arbitrary curved background. It wouldn't make much sense to refer to string theory as a theory of ``quantum gravity'' if strings can only be described on flat backgrounds. The way this is accomplished is by treating the metric of the worldvolume as a ``background field'' $G_{\mu\nu}$, in terms of which the Polyakov action becomes:
\begin{equation}\label{eqn:polyakov-gravity}
	S'_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu}(X),
\end{equation}
where the bulk metric is now a function of the bulk coordinates $G_{\mu\nu}(X)$. Now this metric is still non-dynamical because the action \eqref{eqn:polyakov-gravity} does not contain any terms with time derivatives of $G_{\mu\nu}$. However, if we view the action purely as a two-dimensional theory of $D$ scalar fields, then the bulk metric can be viewed as a collection of \emph{coupling constants}, rather than a dynamical entity which exists independent of the string. One can now proceed in the usual manner for any field theory and calculate the beta function of the coupling constants of the theory as a function of the energy scale.

Then, as shown long ago by Friedan \cite{Friedan1985Nonlinear} (see also \cite{Callan1989Sigma}, \cite{Callan1985Strings} or \cite[Sec 3.7]{Polchinski1998aString}, \cite[Sec 7.2]{Tong2010Lectures} for a more pedagogical explanation), the graviton beta function is proportional to $R_{\mu\nu}$, the Ricci curvature of the bulk geometry. The requirement of Weyl invariance of the string worldsheet implies that this beta function should vanish:
\begin{equation}\label{eqn:ricci-flat}
	\beta(G_{\mu\nu}) \propto R_{\mu\nu} = 0.
\end{equation}
Therefore we find that conformal invariance of the string worldsheet \emph{implies} that the background geometry in which the string propagates satisfies the \emph{vacuum} Einstein equations. It is this result which is often cited as evidence for the claim that string theory is a \emph{background independent} theory of quantum gravity.

@@

There is another explanation for why it makes sense to promote the $X$'s to local fields. This can be found in terms of the expression for the area of a 2-surface. We have a manifold $\mc M$, within which is embedded a two dimensional submanifold $\mc N$. Let $(\tau,\sigma)$ be the location of a point on the worldsheet and $X^\mu(\tau, \sigma)$ be the location of that same point in terms of co-ordinates on $\mc M$. Then we can define the induced metric on $\mc N$, $h_{ab}$ in terms of derivatives of the embedding fields (the pullback):

\begin{equation}\label{eqn:ws-metric}
	h_{ab} = \frac{\partial X^\mu}{\partial x^a} \frac{\partial X^\nu}{\partial x^b} G_{\mu\nu},
\end{equation}
where $G_{\mu\nu}$ is the metric in the ambient space $\mc M$. Now, we can calculate the area of a small patch of $\mc P \in \mc N$ by taking the square root of the determinant of the induced metric $\sqrt{- \det(h)}$ and integrating over that patch:
\begin{equation}\label{eqn:patch-area-v1}
	A^{(1)}_{\mc P} = \int_{\mc P} d^2 x \, \sqrt{- \det(h)}.
\end{equation}
This is, of course, the expression for the Nambu-Goto action - modulo some constants - which we all know and love. In LQG we don't have a notion of embedding fields. Since we are dealing with gauge invariant observables constructed from holonomies of a connection along a 1d-curve and the flux of a tetrad across a 2-surface, the embedding coordinates of the curves and surface turn to not be needed. When promoting classical observables into quantum operators acting on lines and surfaces the embedding coordinates of the lines and surfaces are not relevant as long as we work with gauge invariant quantities.

How then does one define the area of a surface in LQG? It is defined as the magnitude of the area two form. Recall that given a tetradic basis $e_\mu^I$ for a local Lorentz frame whose metric is given by $g_{\mu\nu}$, we can write the metric in terms of the tetrad in the usual manner:
\begin{equation}\label{eqn:metric-from-tetrad}
	g_{\mu\nu} = e_\mu^I e_\nu^J \eta_{IJ},
\end{equation}
where $\eta_{IJ}$ is the flat Minkowski metric on the ``internal'' flat space. If we consider any two dimensional surface in the local Lorentz frame, then its area can be written in terms of the vielbein as:
\begin{equation}
	A^{(2)}_{\mc P} = \int_{\mc P} \Tr (e \wedge e),
\end{equation}
where $e = e_{\mu} \diff x^{\mu}$ and the trace is taken over the ``internal'' Lorentz indices.

Now, if we compare the two expressions \eqref{eqn:ws-metric} and \eqref{eqn:metric-from-tetrad} we notice an obvious parallel between the derivatives $\partial X^\mu/\partial x^a$ of the embedding co-ordinates and the vielbein $e_\mu^I$. This similarity becomes more apparent once we write down the expression for the area of a 2-surface by taking the determinant in \eqref{eqn:patch-area-v1} and comparing that to the expression obtained using frame fields.
